Co-citations in context

### 2019-06-12 cocit_r.tex
fixed first para of Results section

\subsection{Model Misspecification and the Attributes of Disciplinary Context} 
Recall our concern regarding model misspecification  in the Uzzi {\em et al.}~model arising from treating all references in a given year as equiprobable, thus allowing substitutions from WoS without consideration of subject matter (as reflected in the publication's discipline) or citation frequency.
Under this model, the probability of replacing a reference by another reference in a given discipline is identical to the proportion of the articles in WoS that are in that particular discipline.
Thus, if the model accurate reflects citation practice, the proportion of references within papers published in a given discipline $D$ would be the same as the proportion of articles in the discipline $D$, and--conversely--the degree to which the proportion deviates from the expected value reflects the degree of model misspecification.
%due to considering disciplinarily irrelevant references as a concern when disciplinary subsets are analyzed using a random graph model that generates expected co-citation frequencies from the WoS superset. 
%A symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline. 
We therefore  assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods). 
Using the WoS extended classification of 153 subject areas, we then analyzed the disciplinary composition of the references in these three datasets into the five research areas in the Web of Science (life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities) for the years 1985, 1995, and 2005. We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area, which is close to the value of 79.5\% for the references in the physical sciences area. Similarly, 93.7\% and 92.1\% of the references in the immunology and metabolism datasets belonged to the life sciences and biomedicine research area, again close to the value of 89.9\% for the references in the life sciences and biomedicine area. \emph{Add in Sitaram's new data}. 
These data indicate strongly that references are likely to belong to the same research area as the publications that cite them. Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.

\textcolor{blue}{I don't think the paragraph above makes the point that the distribution that is observed is inconsistent with the Uzzi et al. model. But to make that point, it would be nice to know the proportion of publications in each of the five major subject areas. With that information,  I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.
In other words, this is where we want to add the additional data about expected values ~2.5\% for AP as an example.}

>>>>

\subsection{Model Misspecification and the Attributes of Disciplinary Context} A source of misspecification in the Uzzi {\em et al.}~model arises from not accounting for disciplinary heterogeneity by treating all references as equiprobable substituents. Under this model, the probability of replacing a reference in one discipline by another reference in a second discipline is identical to the proportion of the articles in WoS that from the second discipline. If the model approximated citation practice, the proportion of references within papers published in a given discipline $D$ would be expected to be equal to the proportion of articles in the discipline $D$, and--conversely--the degree to which the proportion deviates from the expected value would reflect the extent of model misspecification.

We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).  We used the the WoS extended classification of five major research areas comprising life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities and matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively. We analyzed the composition of the  references in our three datasets according to the five research areas in the Web of Science for the years 1985, 1995, and 2005. We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area,  However, corresponding reference content for the WoS superset was 33.4\% (physical sciences) and 52.9\% life sciences and biomedicine. These data suggest at a high level (i) misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas. Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.

\textcolor{blue}{I don't think the paragraph above makes the point that the distribution that is observed is inconsistent with the Uzzi et al. model. But to make that point, it would be nice to know the proportion of publications in each of the five major subject areas. With that information,  I think this is where we can do a statistical test, and show that these numbers are highly unlikely under the random model.}
